Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-07-27 threshold/draft.Rnw
Commented out spca reference; not needed probably

These steps are formalized in Algorithm \ref{prune} below. The algorithm
proceeds in two main parts: steps 1--6 prune pairs of vectors down to a small
candidate set of vector pairs that may meet the correlation threshold; step 7
computes the correlation values and applies the threshold across the reduced
set of vector pairs.

@@

%% Related use of SVD in other methods
\bibitem{spca}
Bair, Eric, et al. Prediction by supervised principal components. Journal of the American Statistical Association 101.473 (2006).

>>>>

These steps are formalized in Algorithm \ref{prune} below. The algorithm
proceeds in two main parts: steps 1--6 prune pairs of vectors down to a small
candidate set that may meet the correlation threshold; step 7
computes the correlation values and applies the threshold across the reduced
set of vector pairs.

@@

%% Related use of SVD in other methods
%\bibitem{spca}
%Bair, Eric, et al. Prediction by supervised principal components. Journal of the American Statistical Association 101.473 (2006).
